Tropical Mathematics and the Lambda Calculus

### 2023-01-23 section4.tex
Commit notturno (finita parte Taylor)
commit

%Before looking at what happens in the case of non-linear programs, let us make the metric structure of $\LREL$ explicit. 
The following proposition provides a useful characterization of the functional metrics in $\LREL$, relying on 
the bijection between $\HOM{\LREL}{X}{Y}$ and set of tropical linear functions from $\Lawv^{X}$ to $\Lawv^{Y}$.
\begin{proposition}
For all tropical linear functions $f,g:\Lawv^{X}\to \Lawv^{Y}$, $\norm{ \matr f-\matr g}_{\infty} =  \sup_{\B x\in \Lawv^{X}}
\norm{ f(\B x)-g(\B x)}_{\infty}$.\end{proposition}

@@

Using Corollary \ref{prop:polylip}, an immediate consequence of the lines after Theorem~\ref{thm:modelsTaylor} is:

>>>>

%Before looking at what happens in the case of non-linear programs, let us make the metric structure of $\LREL$ explicit. 
The following proposition provides a useful characterization of the functional metrics in $\LREL$, relying on 
the bijection between $\HOM{\LREL}{X}{Y}$ and set of tropical linear functions from $\Lawv^{X}$ to $\Lawv^{Y}$.
\begin{proposition}
For all tropical linear functions $f,g:\Lawv^{X}\to \Lawv^{Y}$, $\norm{ \matr f-\matr g}_{\infty} =  \sup_{x\in \Lawv^{X}}
\norm{ f( x)-g(x)}_{\infty}$.\end{proposition}

@@

Using Corollary \ref{prop:polylip}, an immediate consequence of %the lines after Theorem~\ref{thm:modelsTaylor} is:
Corollary~\ref{cor:T(M)=M} is:
